### 2019-02-05 thesis_report/conclusion.tex
edited intro and concl

% -*- root: ./report.tex -*-
\chapter{Conclusion}
In the model we study, the introduction of a zigzag geometry increases the topological gap by several orders of magnitude while simultaneously reducing the Majorana length.
Additionally, the breaking of a chiral symmetry brings the system from the BDI symmetry class into the D symmetry class, resulting in a cleaner topological phase.  % Bas: how is the symmetry broken?
Together, these improvements directly affect the robustness of the Majorana state, potentially bringing us closer to reliably create topological devices.

\comment{With the current quasiclassical analogy, we are not able to explain the improvements of zigzag.}
The current used quasiclassical analogy, applied in the most lenient form, is not able to fully explain the increased gap of a zigzag system.
Furthermore, numerical simulation points out that the optimal geometry does not always coincide with the minimal trajectory length.
It is therefore unsure whether the improvement of the gap can be fully attributed to the elimination of long trajectories, or if the arising phenomena are due to other mechanisms.
In any case, the improvements are stable under a wide range of parameters, and the topological gap varies gradually as a function of geometry, indicating the effect is not merely coincidental.
Further study should be devoted to isolating the working principle behind the improvements of the zigzag geometry.

\comment{Extensions: we omit several physical effects, disorder, electrostatics, etc.}
In the model used, we omit several physical effects, such as disorder, electrostatics, the orbital effect, etc.  % Bas: what is etc.? Leave it out or write out the other effects
Apart from experimental verification, further study is required to see whether the conclusions of this model are valid.  % Bas: waar komt de onzekerheid vandaan? Waarom is er meer verificatie nodig?

\comment{Current fabrication techniques seem compatible with the proposed geometry, and experimental verification should point out whether it holds up to its promise.}
Current fabrication techniques seem compatible with the proposed geometry, and experimental verification should point out whether it holds up to its promise.
We note that slight modifications to the geometry, for example, to ease measurement, should not have large implications on the physics.
Currently, experimental groups have already fabricated zigzag devices (e.g. the image on the cover of this thesis), and measurements are underway.

\comment{It would be interesting to study what geometry creates an optimal environment for Majorana modes to exist.}
We have studied sawtooth, snake-like, and offset sinusoidal modulation of the semiconductor region, but perhaps a more exotic shape will be optimal. % Bas: note that research in shape optimization is in progress (Andre)
A study optimizing the geometry for supporting Majoranas would be an interesting continuation.

>>>>

% -*- root: ./report.tex -*-
\chapter{Conclusion}\label{chap:conclusion}
In the SNS system studied, the introduction of a zigzag geometry increases the topological gap by an order of magnitude, while simultaneously reducing the Majorana decay length.
Furthermore, the geometric alteration breaks an additional symmetry, bringing the system from the BDI symmetry class into the D symmetry class, resulting in a cleaner topological phase.

Together, these improvements directly affect the robustness of the Majorana state, potentially bringing us closer to be able to reliably create topological devices.
For instance, the improved topological gap allows for an increased tolerance in device manufacturing, as well as providing a clean background for a hopefully present zero-bias peak.
Also, the protection of the system against thermal fluctuations has an exponential dependence on the gap size, and is thus increased by many orders of magnitude.
Furthermore, the reduced Majorana decay length manifests itself in stronger topological protection, and decreases the minimum required coherence length of the semiconductor.

\comment{With the current quasiclassical analogy, we are not able to explain the improvements of zigzag.}
The current used quasiclassical analogy, even when applied in a very lenient form, is not able to fully explain the increased gap of a zigzag system.
A possible reason for the discrepancy is the fact that the quasiclassical model is not able to capture the availability of a wide range of slopes to scatter against: in a straight system, long trajectories coincide with grazing angles.
Furthermore, numerical simulation points out that the optimal geometry does not always coincide with the minimal trajectory length.
This is possibly explained by tunneling of the wavefunction through the superconductor, but as is the case with the grazing angles, further investigation is necessary.

In any case, the improvements are stable under a wide range of parameters, and the topological gap varies gradually as a function of geometry, indicating the effect is not merely coincidental.
Although we cannot exclude the possibility that some other process is responsible for the gap improvement, we still expect the driving mechanism to be the suppression of long trajectories.
We are currently investigating other strategies to confirm this notion.

\comment{Extensions: we omit several physical effects, disorder, electrostatics, etc.}
In the model used, we omit several physical effects, such as disorder, electrostatics, and the orbital effect.
Although the same restrictions hold for the straight geometry, it would be interesting to see whether inclusion of these physical effects amends the conclusions of this thesis.

\comment{Current fabrication techniques seem compatible with the proposed geometry, and experimental verification should point out whether it holds up to its promise.}
Current fabrication techniques seem compatible with the proposed geometry, and experimental verification should point out whether it holds up to its promise.
We note that slight modifications to the geometry, for example, to ease measurement, should not have large implications on the results.
Currently, experimental groups have already fabricated zigzag devices (e.g. the image on the cover of this thesis), and measurements are underway.

\comment{It would be interesting to study what geometry creates an optimal environment for Majorana modes to exist.}
We have studied sawtooth, snake-like, and offset sinusoidal modulation of the semiconductor region, but perhaps a more exotic shape will be optimal. 
Additionally, although not reported in this thesis, similar results are found for zigzag modulation of classic nanowire systems, where the semiconductor is interfaced with only a single superconductor.
A study optimizing the geometry for supporting Majoranas would be an interesting continuation, and is currently being undertaken within the group.

### 2019-02-05 thesis_report/introduction.tex
edited intro and concl

\section{Thesis structure}
	In this thesis we show that the introduction of a zigzag-shaped modulation of the junction region leads to an order of magnitude increase of the topological gap, as well as a significant reduction of the Majorana decay length.
	The proposed alteration of the geometry has the potential to eliminate the problem of a soft gap, whilst staying compatible with current fabrication methods.
	Additionally, the reduction of the Majorana decay length allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets a limit for the device size.

	Furthermore, we try to establish the working mechanism behind the improvements: we hypothesize that the gap improvement is the result of the elimination of long trajectories.
	In order to verify this claim, we propose a simplified model of the zigzag system such that we can isolate the dependence of the gap on the length of available trajectories.

	In Chapter \ref{chap:theory}, we give an overview of established theory relevant to the understanding of this thesis.
	Subsequently, in Chapter \ref{chap:methods} we discuss the various methods used for the analysis of zigzag systems, of which the results are discussed in chapter \ref{chap:results}.
	Finally, in Chapter \ref{chap:conclusion} we discuss the findings of this thesis, as well as provide an outlook on further research to be performed.

>>>>

\section{Thesis structure}
	In this thesis we show that the introduction of a zigzag-shaped modulation of the junction leads to an order of magnitude increase of the topological gap, as well as a significant reduction of the Majorana decay length.
	The proposed alteration of the geometry has the potential to eliminate the problem of a soft gap, whilst staying compatible with current fabrication methods.
	Additionally, the reduction of the Majorana decay length allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets the limit for the device size.

	Furthermore, we try to establish the working mechanism behind the improvements: we hypothesize that the gap improvement is the result of the elimination of long trajectories.
	In order to verify this claim, we propose a simplified model of the zigzag system such that we can isolate the dependence of the gap on the length of the trajectories.

	In Chapter \ref{chap:theory}, we give an overview of established theory relevant to the understanding of this thesis.
	Subsequently, in Chapter \ref{chap:methods} we discuss the various methods used for the analysis of zigzag systems, of which the results are discussed in Chapter \ref{chap:results}.
	Finally, in Chapter \ref{chap:conclusion} we discuss the findings of this thesis, as well as provide an outlook on further research to be performed.
